---
title: "linreg"
author: "Clara Schartner and Araya Eamrurksiri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package `linreg` includes a function `linreg_function` for linear regression. 

## Background
The linear model:
$Y = X\beta + \epsilon$

The regression coefficient $\beta$ is calculated according to the method of the least squares.
$\hat{\beta} = (X´X)^{-1}X´X$

## Functions



```{r, echo=FALSE}
library(linreg)
data("faithful")
```
By using the function `linreg` a linear model is calculated.

```{r}
lin.result<-linreg_function(waiting~eruptions,faithful)
lin.result
```
In the output the results of the coeffients is shown together with the input formula.
```{r}
residuals<-resid(lin.result)
head(residuals)
```
In order to obtain more information about this linear regression, the results of the linear regression are saved. 
Then there are a couple of functions which help to learn more about the results of the regression.
The function `predict` returns all the predicted values.
```{r, eval=FALSE}
predict(lin.result)
```
The function `coef` returns only the coefficients, which can be useful if you need to coefficients for further calculations.
```{r}
coef(lin.result)
```
Using `summary` is very useful to get more information about the fit of the linear regression.
You get the coefficients together with the standard errors, the t-value and the exact p-value.
The degrees of freedom are also gotten from the output.
```{r}
summary(lin.result)
```
If you plot the results of the linear regression you get two plots: 
One showing the fitted values vs. the residuals together with a lowess of fit curve.
The other plot shows the fitted values vs. the root of the absolute value of the standardized residuals.
```{r, fig.show='hold'}
plot(lin.result)
```



